---
title: "Grouping and summarizing"
author: "Steve Huguenin"
date: "2025-10-13"
format: pdf
output: html_document
pdf-engine: lualatex
papersize: a4paper
embed-resources: true
editor: source
---


### Identify the duplicated row
Identify the duplicated subject.

### Compute basic statistics for all moral dilemma columns. 
Compute the mean, the median, the standard deviation as well as min and max values.
Find meaningful short names for the functions such as `med` for  the median.

Assign `judgments_condition_stats` to the results.

```{r}
library(tidyverse)
judgments <- read_tsv("https://biostat2.uni.lu/practicals/data/judgments.tsv")
judgments_condition_stats <- judgments |>
  mutate(
    across(matches("^moral_dilemma"), list(avg = mean, med = median, std = sd, min = min, max = max)),
    .keep = "none"
  )
judgments_condition_stats
```



### Sort by groups

Find the number of subjects by `age`, `gender` and `condition`, e.g. how many 20 years of age females are in the `stress` group. 

Sort the resulting tibble such that the condition that contains the most populous group is sorted first (i.e. `stress` or `control` appear together). 

```{r}
judgments |>
  group_by(age, gender, condition, .add = FALSE, .drop = TRUE) |>
  tally(sort=TRUE)
```

Ensure that the resulting tibble does not contain groups.




